Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-11 providence/sections/pilot.tex
more pilot discussion

We can use simulations to better understand typical audit behavior for the margin of this pilot audit and contextualize the results we obtained in the pilot. We run $10^4$ trial audits for several stopping probabilities $p$. Each round size is chosen to give a probability of stopping $p$ assuming the announced tally and given the results of previous rounds. We use the same $10\%$ risk limit and margin of $25.57\%$. Figure~\ref{fig:pilot_sims} shows the average number of ballots sampled for each value of $p$.

Section~\ref{sec:workload} addresses more appropriate measures of workload

>>>>

We can use simulations to better understand typical audit behavior for the margin of this pilot audit and contextualize the results we obtained in the pilot. We run $10^4$ trial audits for several stopping probabilities $p$. Each round size is chosen to give a probability of stopping $p$ assuming the announced tally and given the results of previous rounds. We use the same $10\%$ risk limit and margin of $25.57\%$.

Figure~\ref{fig:pilot_sims} shows the average number of ballots sampled for each value of $p$ in the simulations. The vertical line denotes the stopping probability of the first round size chosen in the pilot of $140$ ballots. The average number of ballots for such a high stopping probability round schedule is high. blah blah based on plot and some numbers illustrating that point... Of course, average number of ballots is not the only metric that matters when planning an audit. For this pilot audit, extensive planning of the round schedule was not necessary because the margin was high enough the relatively few ballots were needed even to achieve the high probability of stopping. In Section~\ref{sec:workload} we consider a larger, state-wide contest where selecting the round schedule has more significant implications. Some of the ideas introduced in Section~\ref{sec:workload} we do apply to this pilot case as well.
